\documentclass[char]{Katmeers}
\begin{document}
\name{\cCrabbe{}}

\updatemacro{\cHarry}{
  \nickname{Drew Carpenter}
  \mapnickinformal
}

Your life, before you became enlightened, was fairly typical. You're the youngest child of a prominent wizarding family, and like all your fore bearers, you were sorted into Lanayru House. You did well in school, and had a particular gift for divination and seeing the unseen. You always had a particular connection with the Katmeers ghosts. In your misguided struggles against Thevardra, the ghosts aided you with reconnaissance and sundry other tasks, in exchange for favors of various sorts. You were that quietly friendly kid, like a budding guru, who got along with pretty much everyone, including - in a kind of odd, grudging way - the Eldin crowd, who otherwise did not associate with people outside their own House. You were even the Eldin \cLucius{}'s appointed confidante, which was a mixed blessing due to \cLucius{\their} rather arrogant nature, but you believed you could see the good underneath and worked hard to bring it to the fore. You were also sort of the shepherd of the Katmeers ghosts during your time at school; you helped them with their ghostly problems, and they helped you as they could in the fight against the Endless.

But at the final battle, you had the revelation. Despite the fact that you, like everyone else, saw Thevardra destroyed by \cHarry{}, you alone also saw a crumb of her essence fly away from her. And then you realized. The others were wrong. Thevardra really is Endless. She cannot be destroyed, not even by the greatest \cHarry{\hero} of all time, wielding the power of the Paragons. And this, she is inevitable. It is pointless to struggle against her. The only hope that anyone has is to appease her, and be one of those that she helps to ascend. The more you thought about this, the more right it seemed. And so your course was set. You would faithfully serve Thevardra, and when she inevitably rose again, you would be one of those who was saved. And the more you thought about it, the more you realized that the Dark Lady had been right all along. Courage and wisdom are just masks for the truth: in the end, all there is is power, and those too weak to understand it.

You set about looking for others who shared your convictions, and you came to know that your Eldin classmate \cGoyle{} was still a follower of Thevardra, and you recruited \cGoyle{\them} to help you resurrect her. Somehow the two of you have managed to avoid the watchful eyes of the Aurors. You knew that you would need a lot of currency, and you knew where you could get it. Framing \cLucius{} as one of the Endless was child's play, especially as both of \cLucius{\their} parents were know allies of the Dark Lady, and so very many students of House Eldin had fallen under her sway. After that, you only had to get the key to \cLucius{\their} vault at Gingotts, and you had access to all of \cLucius{\their} family's vast and vaunted wealth.

Getting to the key involved the use of your second and rather more dubious ally. In the arcane backlash that followed Thevardra and \cHarry{}'s duel, many wizards lost their minds, and it was immediately obvious to you that one of these unfortunates was \cGinny{}. \cGinny{} fervently believes that the ghosts are trying to tell \cGinny{\them} something. They're not, but you have been able to use your position as Katmeer's resident medium to dangle \cGinny{\them} along, getting \cGinny{\them} to use her significant thieving abilities in exchange or communication with \cGinny{}'s dead friends. \cGinny{} is most desperate to speak with \cHarry{}, of course, as they were something of an item before \cHarry{\their} death. But you've never managed to find \cHarry{\their} ghost. You can only assume that \cHarry{\they} was annihilated in the arcane explosion as everyoen said - \cHarry{\they} was not, after all, Endless. So you lie to \cGinny{\them}, and tell \cGinny{\them} that \cHarry{\they} is talking to you. It's a pretty easy way to get \cGinny{\them} to do whatever you need \cGinny{\them} to.

You are here tonight because the ghosts told you that the Paragons would all be here tonight. If you could unite the Paragons, you cold revive Thevardra, and surely your reward would be great. Furthermore, you have uncovered the possibility of another potentially powerful ally. Your housemate, \cHermione{}, it seems, has likewise come to understand the primacy of Power, and has become Dark \cHermione{\them}self. Amonst the back alleys where the Dark wizards congregate, there are persistent and credible rumors that \cHarry{}'s former friend has been dabbling in all manner of unsavory matters, including the nearly lost art of Necromancy. But you are cautious. While an ally amongst the Aurors would be of great use, and of course a necromancer would be very valuable to your cause, you are not sure whether or not \cHermione{\they} can really be trusted to assist the new Endless, or if \cHermione{\they} has merely been pursuing Dark magic for \cHermione{\their} own purposes.

\begin{itemz}[Goals]
	\item Help \cGoyle{\formal} unite the Paragons and revive Thevardra.
	\item Keep \cLucius{} from finding out you were the one who framed \cLucius{\them}.
	\item Keep \cGinny{} from finding out that you've been lying to \cGinny{\them}.
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	\contact{\cGinny{}} Your most useful tool, \cGinny{} is an expert thief who believes that you are her bridge to the world of the ghosts, which \cGinny{\they} claims \cGinny{\they} can faintly hear. However, \cGinny{\they} is simply hallucinating, and has been for a decade.
	\contact{\cHermione{}} Your fellow Lanayru, who may likewise have found enlightenment. On the other hand, \cHermione{\they} is married to a Muggle, which does not immediately suggest sympathy with the Endless creed.
	\contact{\cLucius{}} You used to be \cLucius{}'s confidant, but you see now that \cLucius{\they} is a weak and unworthy \cLucius{\human}, always standing in the shadow of other's greatness. \cLucius{\Their} family fortune funds your current endeavors, which is probably the most useful thing \cLucius{} has accomplished in \cLucius{\their} life, however accidentally.
	\contact{\cGoyle{}} Your partner in the endeavor to raise the Dark Lady. \cGoyle{\They} is more cunning that you think anyone realized, and truly is worthy of the Endless.
	\contact{A Ghost} You don't know whose ghost it is, but it seems more focused and more powerful than the others. You surmise that \cGhost{\they} died relatively recently - probably a casualty of the Battle of Katmeers.
\end{contacts}

\end{document}