\documentclass[char]{Katmeers}
\begin{document}
\name{\cFairy{}}

\updatemacro{\cHarry}{
  \nickname{Drew Carpenter}
  \mapnickinformal
}

\bigquote{This is how the trouble started.}

You were just like any other fairy, living in a magical fountain under the leadership of the puissant but draconian Great Fairies. being a fairy is often a hard lot. You never really left your fountain, as the Great Fairies had forbidden it, and the only time you ever saw people outside the other fairies of your fountain was the occasional adventurer who would stop by in need of healing while on one quest or another. But it didn't occur to you that things could be any other way until one day, a wizard named \cMalfoy{\formal} came to your fountain and caught you in a bottle. \cMalfoy{\They} then gave it to \cMalfoy{\their} \cMalfoy{\offspring}, \cMalfoy{}, and you were charged with protecting \cMalfoy{\them}. \cMalfoy{\They} carried you around for years, and through the glass of the bottle, you saw an endless stream of tantalizing images of the world outside your fountain. And then \cMalfoy{} was gravely injured in a fight against another young wizard named \cHarry{}, and as is the usual contract, \cMalfoy{} released you from the bottle, you healed \cMalfoy{\them} and you were pulled back to your Fountain. But you were left with a powerful yearning to explore the strange and wonderful world that you had glimpsed through the bottle.

One of the things that fascinated you so much about the outside world was the entire concept of possessions. The only objects at the Fountain were some piles of bombs that the Great Fairy kept to give to aspiring adventurers that she favored - and of course, a lowly fairy like yourself was forbidden to touch them. Your young master and all the people \cMalfoy{\they} interacted with had so many strange and beautiful things around them all the time. You loved those things. You loved them so much. You want all of them to be yours. You dream of keeping them all in a giant room so that you can roll around in them, the pretty shiny things. And you thought to yourself, ``Man, adventurers have all the cool things. Maybe you should become an adventurer, and then you could ahve beautiful things all to your self, just like \cMalfoy{\formal} had!''

So you grabbed a few piles of bombs to start your collection of adventuring spoils, and you left the fountain. But you quickly realized two things: first, you had no idea how to be an adventurer. The steps between declaring yourself the world's first fairy adventurer and receiving the vast wealth that adventurers all seem to end up with were a mystery to you. Second, you realized that, after having stolen a large number of treasures from the Great Fairy, you were now a criminal. If you ever return to your fountain, you will face the Great Fairy's terrible wrath. You don't like to think what she'll do to you.

Fortunately for you, as you were wandering lost through an eldritch forest, a solution to your problems appeared: you met a wandering \cNeville{\magician} named \cNeville{}. \cNeville{\they} was an adventurer, and you thought, maybe \cNeville{\they} could teach you to be an adventurer too! So you've been following \cNeville{\them} around, and you are deeply devoted to \cNeville{\them}. But it's clear that although \cNeville{} is very brave, and is saving the world, \cNeville{}'s kind of unobservant, and doesn't know a lot of important things about the world. But that's okay -- you do! For example, once when you were in an ancient desert, you found the \iWisdom{\MYname}, and it chose \cNeville{\them} as it's wielder -- but \cNeville{\they} didn't know much about it, and you were able to fill \cNeville{\them} in. It's the perfect relationship - \cNeville{\they} saves teh world, and you make sure \cNeville{\they} knows everything \cNeville{\they} needs to know in order to do so. And along the way, there is ample opportunity to acquire treasure enough for both of you!

The only difficulty is that \cNeville{} has a tendency to be absent-minded, unobservant, and a bad listener. It's okay. You know that means you need to work extra hard to make sure \cNeville{\they} listen to all of your great wisdom. Sometimes you need to repeat yourself three, four, five, or more times to make sure \cNeville{\they} hasn't missed anything vital. But despite this, you admire \cNeville{\them} a lot. And you care about \cNeville{\them} a lot.

\cNeville{\They} really wanted to come to this gathering. It's part of \cNeville{\their} quest to save the world, and so you're here to keep \cNeville{\them} out of trouble. \cNeville{\They}'s told you a fair amount about each of these people, and everything taht happened while \cNeville{} was at school. All fascinating, heroic stuff. You look forward to meeting them all in person. Well, almost all. You don't like the affection with which he always talks about \cGinny{}. What's \cGinny{\they} got that you don't? You'll show \cGinny{\them}; you are going to be the most helpful, useful, knowledgeable companion ever.

\begin{itemz}[Goals]
	\item Protect \cNeville{}
	\item Show \cNeville{} and everyone else that you are better than \cGinny{} in every way.
	\item Acquire treasure. It occurs to you that if you acquired all three Paragons, you could become human and thus never have to return to your fountain again and also be on equal footing with \cNeville{} and maybe you two could get married or something - but that would mean acquiring \cNeville{}'s Paragon, possibly even stealing it. It's up to you whether or not you are willing to take such a potentially treacherous step.
\end{itemz}

\begin{itemz}[Notes]
	\item You don't have any items. Yet.
	\item In order to use your combat abilities [abilities who have a Priority Number (ie: P1)], you {\bf must} say the ``triggering phrase'' associated with each ability in order to use it. The ``Triggering phrase'' is the name of the ability.
\end{itemz}

\begin{contacts}
	\contact{\cNeville{}} Your constant companion, whom you are wildly in love with. \cNeville{\they} has shown you a whole brilliant new world,  but \cNeville{\they} tends to be absent minded, and thus needs you as much as you need \cNeville{\them}.
	\contact{\cGinny{}} You just met \cGinny{\them}, but you hate \cGinny{\them}. Also, just from looking at \cGinny{\them}, you can tell that \cGinny{\they} is completely insane.
	\contact{\cMalfoy{}} \cMalfoy{\They} carried you around in a bottle for a few years, before you saved \cMalfoy{\their} life and went home. On the one hand, without \cMalfoy{\them} you would never have known how beautiful the world outside the fountain was. ON the other hand, being stuck in a bottle was kind of a frustrating way to live. 
\end{contacts}

\end{document}