\documentclass[char]{Katmeers}
\begin{document}
\name{\cGhost{}}

\updatemacro{\cHarry}{
  \nickname{Drew Carpenter}
  \mapnickinformal
}

From a young age, your parents used to tell you that you would never amount to anything. You were something of a lazy delinquent, and your parents didn't really care enough about you to push you to work hard. You were ambitious in your own way, but your strategy was always to attach yourself to someone who was going places, and ride their coattails all the way to success. It was this shared trait that brought you together with \cGoyle{\formal}, your associate since childhood. (People used to assume that ou were dating \cGoyle{\them}, but it's never been like that with yo two. \cGoyle{\They}'s more like a \cGoyle{\sibling}.) When you arrived at Katmeers you both immediately identified \cMalfoy{\formal} as the perfect person to carry the two of you all the way to the top. \cMalfoy{\They} was cunning and vicious, but \cMalfoy{\they} needed some muscle to get his dirty work done, and that was where you came in. You were all sorted into Eldin, and you can't imagine it having gone down any other way.

The later years at Katmeers were a time of turning for you, though. As a child you had always been unquestioningly loyal to \cMalfoy{\formal} and \cGoyle{\formal}, but as you grew older, you became increasingly uncomfortable with how they were being pulled deeper and deeper into the clutches of the Endless. Your parents were wizards, but three of your grandparents were Muggles, and you couldn't avoid the feeling that if Thevardra had risen a few hundred years ago, you never would have been born. things were further complicated by the fact that somewhere in your fifth year, you realized that you were obsessed with \cHermione{}. How could you not be? \cHermione{\They} was just so cool, like the \cHermione{\hero} in a storybook, handling every problem that came \cHermione{\their} way with perfect poise and a clever quip. You wanted to be just like \cHermione{}, but could never quite find the  effortless joy in knowledge that \cHermione{\they} seemed to have. Failing that, you wanted to impress \cHermione{\them}, and you were pretty sure that becoming one of the Endless would do the exact opposite.

Nonetheless, you were pulled along in \cMalfoy{\formal} and \cGoyle{\formal}'s wake for a long time. Eventually you realized that \cMalfoy{\formal} was as conflicted about \cMalfoy{\their} allegiance to the Dark Lady as you were, and you hoped that \cMalfoy{\they} would snap out of it and lead you back towards some path you didn't feel embarrassed to admit that you were on. But although you could tell that \cMalfoy{\they} was teetering on the brink of breaking with the Endless, \cMalfoy{\they} seemed incapable of taking the final step. Even at the final battle, \cMalfoy{\they} dithered on a balcony, not able to decide which side to join on. Meanwhile, you could see \cHermione{} in the thick of it, beautiful and brave, fighting for the side that might be doomed but was clearly in the right. And finally, for the first time, you made a choice on yor own - you raised your wand to assist in \cHermione{\their} defense.

You had approximately two seconds of the most giddy feeling of empowerment and heroism you ever felt in your life, and then someone behind you murdered you. \cMalfoy{\formal} had clearly chosen sides at last.

And then you were a ghost, looking down at your body lying in the shattered rubble of the balcony you had been standing on. You could see \cMalfoy{\formal} gazing in feigned horror at the edge of the remaining balcony and \cGoyle{\formal} nearly collapsing in grief next to him. You could see \cHermione{}, still valiantly trying to defend all of \cHermione{\their} close allies with \cHermione{their} Patronus. And then there was the terrible flash of arcane backlash as Thevardra and \cHarry{} mutually destroyed each other, and you dn't remember anything for a while after that.

Many of your classmates became ghosts after the battle, but many of them have faded now, lacking sufficient passion to hold them to the living world. You are sustained by your anger over \cMalfoy{\formal}'s betrayal and your hero-worship of \cHermione{}. You haven't seen either of them in a decade, but you eavesdrop on the current faculty of the school and have managed to more or less keep up with the news. You were deeply pleased when you heard that \cMalfoy{\formal} was forced to flee the wizarding world. (Though you're still angry that \cMalfoy{\they} somehow managed to avoid being sent to Lon-Lon.) You were horrified when you found out that \cHermione{} had married a Muggle. It's the only thing \cHermione{\they}'s ever done that you didn't think was wonderful.

And now \cHermione{\they}'s back - both of them are. It's your best chance to thy to make some sort of sense out of the situation. Perhaps you should try to enlist \cCrabbe{} as an ally in this - \cCrabbe{\they} can see ghosts and \cCrabbe{\they} was considered the perfect confidant. Furthermore, through your ghostly attunement to the arcane, you are also aware that all three Paragons are present at the reunion. It's a true long shot, but if you could somehow get all three Paragons in one place and find a sympathetic person to wield them, perhaps you could be brought back to life. And then you would just need to break up \cHermione{} and \cHarry{\MYname} (seriously, what kind of a name is \cHarry{\MYname} anyhow?) and all could be right with the world.

\begin{itemz}[Goals]
	\item Get resurrected.
	\item Break up \cHermione{} and \cHarry{\MYname}.
	\item Earn \cHermione{}'s friendship.
	\item Find out what \cMalfoy{\formal} is up to and put a stop to it.
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	\contact{\cHermione{}} The most wonderful \cHermione{\human} in the entire world. Just admiring \cHermione{\them} from a distance saved you from becoming Endless like practically all the rest of House Eldin.
	\contact{\cCrabbe{}} You were on reasonably good terms with \cCrabbe{} when you were alive and you'd like to trust \cCrabbe{\them} now that you're dead.
	\contact{\cMalfoy{}} Your former leader, who murdered you at the Battle of Katmeers. You will never forgive \cMalfoy{\them}. Hating \cMalfoy{\formal} keeps your spirit anchored in this world.
	\contact{\cGoyle{}} Your former best friend, back when you were alive. You've missed \cGoyle{\their} companionship; for so long you felt like \cGoyle{\they} was the only one who really understood you. It looks like \cGoyle{\they} has forsaken \cMalfoy{\formal} now, and you are very glad of that.
	\contact{\cHarry{\MYname}} \cHermione{}'s Muggle \cHarry{\spouse}, hwo can't possibly be worthy of \cHermione{\them}. A \emph{Muggle} for Din's sake! Preposterous. Oddly, for a moment you thought that \cHarry{\they} saw you earlier. But that would be impossible - wouldn't it?
\end{contacts}
\end{document}