\documentclass[char]{Katmeers}
\begin{document}
\name{\cGinny{}}

\updatemacro{\cHarry}{
  \nickname{Drew Carpenter}
  \mapnickinformal
}

You can hear the ghosts calling to you. All the time, just at the edge of perception, you can hear your murdered classmates - so many of htem, so many! - crying, screaming, raging, pleading. But you cannot understand them. Their words are lost to you, just as they are. Prominent amongst them, you can always make out a voice that you know is \cHarry{}'s. \cHarry{\They} calls to you across the void, trying to tell you something, something important, something for your ears alone. But you cannot understand even \cHarry{\them}. You can feel \cHarry{\their} love for you, echoing again and agai throughout all of reality, but you are certain that wahtever \cHarry{\they} is tryng to tell you, it is something more than that, because you know that \cHarry{\they} knows you already know how much \cHarry{\they} loves you, as you hope \cHarry{\they} knows how much you love \cHarry{\them}.

You, together with your twin \cRon{\sibling} \cRon{}, are the middle children of a large but not terribly important wizarding family. Both of you are fairly average at wizarding, but you excel in another area. You are really good at sneaking around, and sleight of hand, and going unnoticed. Thieving; essentially, but you always employed your skills in the service of good causes. You were not really one of \cHarry{}'s friends at first - you were too awed by \cHarry{\their} heroic victory over Thevardra as a child. But slowly you realized that \cHarry{\they} could use your skills in \cHarry{\their} quest to defeat the Endless One for good. Once you got over your timidity, the two of you grew close, and eventually you both realized that you loved each other. When \cHarry{\they} was off with \cRon{} and \cHermione{} trying to find the Paragons before Thevardra could, you were holding down the fort at Katmeers with your house mate \cNeville{}, rallying the students to \cHarry{}'s cause, redying them for the battle to come. You saw \cHarry{} briefly before the final battle. \cHarry{} looked like \cHarry{} wanted to say something, but didn't know how. Instead you just told \cHarry{\them} you loved \cHarry{\them}, you kissed \cHarry{\them}, and told \cHarry{\them} \cHarry{\they} could tel you afterwards.

But then everything went wrong. You went to fight in the final battle, leading your classmates with all the courage of your House, and \cHarry{} went to duel Thevardra for the fate of the world. But so many under your leadership fell that day, and then \cHarry{}\ldots{} You were watching \cHarry{\them} fight the Dark Lady, and then there was the most horrible flash of light, and you were falling and falling and you could hear the screams of all your classmates all around you and you heard \cHarry{} cry your name, and then when you woke up, it was three months later and you were in the hospital. And you've heard the screams of the ghosts ever since. But you cannot understand them.

Fortunately, your good friend \cCrabbe{} can. \cCrabbe{} was always sensitive to ghosts and Thestrals, and other invisible things, and \cCrabbe{\they} helps you make sense of what the ghosts are telling you. You don't know what you'd do without \cCrabbe{\them}, honestly. Without \cCrabbe{\their} assistance in unravelling what the ghosts need, you would go mad. Sometimes, in return, \cCrabbe{\they} needs you to perform small tasks for \cCrabbe{\them}, and you are always happy to oblige. The details are lost to you now; like so many other memories, they disappear i the swirl of the ghosts' frantic, incoherent need. You remember something about a key one time? With a fish on it? And another time there was a pair of gauntlets made of gold? Or maybe you only dreamed it.

Even with \cCrabbe{}'s generous help, you are aware that there remains a problem. Whatever \cHarry{} is trying to tell you, it is clearly too private even to be shared with \cCrabbe{}. You need to find some way of communicating with \cHarry{\them} yourself, so that at long last you may know what message it is that \cHarry{\they} has been trying to tell you all this time.

Meanwhile, you are worried about your \cRon{\sibling} \cRon{}. \cRon{\They} has managed to accomplish the amazing feat of becoming Minister of Magic, but there are a lot of nasty rumors floating around that \cRon{\they} spends far more time drinking than \cRon{\they} does governing the wizarding world. \cRon{\They} does seem to drink a lot whenever you're around \cRon{\them}, and you have the sinking feeling that the rumors are true. You need to convince \cRon{\them} to shape up, since you know that \cRon{\they} was really putting \cRon{\their} heart into his Ministry, \cRon{\they} would be a great Minister - the one that this post-Thevardra age so desperately needs.


\begin{itemz}[Goals]
	\item Find out what \cHarry{} has been trying to tell you all this time.
	\item Help \cCrabbe{} with anything \cCrabbe{\they} needs you to do. \cCrabbe{\They} is your best friend, after all.
	\item Try to cheer up Dirk.
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	\contact{\cRon{}} Your twin \cRon{\sibling} and your favorite sibling. You believe in \cRon{\them}, even if no one else does.
	\contact{\cNeville{}} \cNeville{} was your partner in rallying and leading the students of Katmeers during your last year at school. \cNeville{\They}'s a good \cNeville{\human}. You trust \cNeville{\them} almost as much as you trust \cCrabbe{}. But not quite.
	\contact{\cCrabbe{}} Your most trusted and reliable friend since \cHarry{} died. \cCrabbe{} is your link to the world of the ghosts and the only one who can make sense of their cacophonous screaming.
\end{contacts}

\end{document}