\documentclass[char]{Katmeers}
\begin{document}
\name{\cGoyle{}}

\updatemacro{\cHarry}{
  \nickname{Drew Carpenter}
  \mapnickinformal
}

From a young age, your parents used to tell you that you would never amount to anything. You were something of a lazy delinquent, and your parents didn't really care enough about you to push you to work hard. You were ambitious in your own way, but your strategy was always to attach yourself to someone who was going places, and ride their coattails all the way to success. It was this shared trait that brought you together with \cGhost{\formal}, your associate since childhood, and when you arrived at Katmeers you both immediately identified \cMalfoy{} as the perfect person to carry the two of you all the way to the top. \cMalfoy{\They} was cunning and vicious, but \cMalfoy{\they} needed some muscle to get his dirty work done, and that was where you came in. You were all sorted into Eldin, and you can't imagine it having gone down any other way.

You guess most of your classmates think of your seventh and final year at Katmeers as a kind of special hell that they all went through, but not you. \cMalfoy{\formal} was recruited into the Endless by his parents, and that dragged you and \cGhost{\formal} along. But in Thevardra's company, you began to understand true power. \cMalfoy{\formal} had never really treated you with respect, but Thevardra did. She would speak with you alone sometimes, about your potential for greatness, something you had never before believed you could possibly have. She granted you authority over the  other students at Katmeers - a position of actual authority for the first time in your life. Suddenly you were no longer a lackey of a minion. You were somebody. your own ambition finally awakened, and it was dizzying.

You loved her. You loved her the way you never really loved your parents. And she loved you as if you were her son. Before the final battle, she told you that she doubted \cMalfoy{}'s loyalty, and that you were to stay with \cMalfoy{\them}, to keep \cMalfoy{\them} from becoming a traitor. You vigilantly watched \cMalfoy{\them} during the battle, but he did nothing to thwart the Dark lady. He stood on the balcony and watched everyone die, like the ice-cold badass that he was. But \cGhost{\formal}! \cGhost{\formal} attempted to interfere with the Dark Lady's rituals and you, horrified by the betrayal by someone so close to you, shattered the balcony underneath \cGhost{\them}, and \cGhost{\they} fell to \cGhost{\their} death. Sometimes, when you are alone at night, you feel guilty about this. but then you quiell that. You don't need to have any guilt over rooting out and crushing treachery.

When Thevardra was annihilated, for the briefest instant she touched your mind. ``\cGoyle{\formal}'' she whispered, in a voice amazingly serene, ``\cGoyle{\formal}, my chosen heir, Ihave left my power in the world for you. One of my followers has taken it somewhere safe. Follow him to to the desert, claim your legacy, and finish my works as I could not.'' And then she was gone.

Claiming you were just following \cMalfoy{\formal}'s orders, you managed to avoid being thrown into Lon-Lon like so many of your housemates were. Doing so was very painful for your newfound pride, but you could hardly fill Thevardra's shoes while trapped in a high security prison. A free man, you turned your attention towards fulfilling the destiny that Thevardra had gifted you. Which turned out to be an extremely challenging task. You tracked the bearer of Thevardra's shard to an ancient shifting desert, but when you found the man, he was dead, and there was no sign of the shard anywhere.

You're not going to let that little set-back daunt you, though. If Thevardra believed you could do this, you can do this. You've assembled a little cabal of allies, most notably the Lanayru \cCrabbe{}, who apparently decided after the final battle that Thevardra's return and ascendancy was inevitable and \cCrabbe{\they} wanted to be on the winning side. You will be the winning side, and though you intend to initially use the Paragons to gain omnipotence and immortality yourself, of course the next step would be to return your beloved Queen to the world again, and the reward all those who had been loyal to the Endless cause with the deathless state they ahd desired.

\cCrabbe{} also brought along \cCrabbe{\their} best friend \cGinny{} who went quite, quite mad in the arcane backlash following Thevardra and \cHarry{}'s demise. \cCrabbe{} can talk to ghosts, and acts as a conduit by which \cGinny{} can talk to the ghost of \cHarry{}, \cGinny{\their} deceased \cHarry{\significant}; you are aware that \cCrabbe{} must be filtering what \cHarry{} sayas, since everything that \cCrabbe{} relays is rather inconsequential. \cGinny{} is nonetheless, pathetically grateful for such scraps, and \cGinny{} is a very useful addition to your following. \cGinny{\They} is an extremely accomplished thief, and lured on by the prospect of more communication with \cGinny{\their} lost love, \cGinny{\they} follows \cCrabbe{}'s - and by extension your - commands unquestioningly. You're enterprise is being funded with money that \cGinny{} recovered from the family vaults of families sent to Lon-Lon. There's poetry in that you think: Building your new empire out of the ashes of those who tried and failed before you.

You're here tonight because you heard a rumor that one of the Aurors had been seen in the desert shortly before you got there, and you suspect they may have killed the bearer of Thevardra's wrath. You have a handful of classmates who are Aurors, and you figure if wasn't one of them, then they probably know who it was, and then you can find that person and find out what became of your legacy. You suspect it was \cNeville{} of Faron house, who has been particularly zealous about tracking own any remaining Endless. You should probably take \cNeville{\them} out, just so \cNeville{\they} doesn't get in your way once you make your move.

\cCrabbe{} tells you that \cCrabbe{\they} can sense that the Paragons are all present at Katmeers tonight. This might even be a higher priority than the shard - how often are all the Paragons in one place? With the shard and the Paragons, you would literally be unstoppable. You've got your work cut out for you this evening.

\begin{itemz}[Goals]
	\item Recover the shard of Thevardra's wrath.
	\item Acquire the Paragons. Especially the Paragon of Power, which is yours by right.
	\item Use the Paragons to become immortal and omnipotent, and return Thevardra to the world.
	\item Get \cNeville{} killed.
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	\contact{\cGinny{}} A useful tool for your cause, whom \cCrabbe{} handles for you. You try not to have much to do with \cGinny{\them}; \cCrabbe{} tells you that \cGinny{\they}'s not aware of \cCrabbe{\their} allegiances, adn you don't want to risk \cGinny{\them} tattling to \cGinny{\their} Auror friends.
	\contact{\cCrabbe{}} Your ally, although you've been lying to \cCrabbe{\them} a little bit. You're sure \cCrabbe{\they} will understand when \cCrabbe{\they} finds out, though.
	\contact{\cMalfoy{}} Your former ringleader. You have no interest in following anyone else ever again, but you'd be happy to have such a ruthless and calculating \cMalfoy{\human} as a member of your cabal. 
\end{contacts}

\end{document}