\documentclass[char]{Katmeers}
\begin{document}
\name{\cHarry{}}

\updatemacro{\cHarry}{
  \nickname{Drew Carpenter}
  \mapnickinformal
}

You are the \cHarry{\Kid} Who Lived, the Hero Chosen by Fate, the one who was destined to defeat Thevardra Lefours and save the wizarding world from the terrible corruption that she represented. You were practically physically marked by this destiny; the scar from when the Queen of the Endless tried to kill you is vividly prominent on your forehead. You discovered you were a wizard at the age of 10 when you were chosen by the Paragon of Courage as it's Wielder - a heavy responsibility for any wizard, but most especially for an untried child. But somehow you defeated Thevardra, shattering her with the raw power of the Paragon which was wielding you far more than you were wielding it. And then you went to school.

Celebrity is practically as heavy a burden as the paragon itself, and you struggled a bit to find acttual friends as opposed to groupies. But you eventually fell in with \cRon{}, a fellow Faron, and \cHermione{}, a clever Lanayru, and the three of you became inseparable companions. Which is a good thing, because you soon began to see portents, clues, and hints that while you had destroyed Thevardra's physical form, her spirit lived on, reconstructiong her network of followers, seeking to reincarnate herself  and carry on her dark wor. Your friends eagerly volunteered to help you defeat her again, and for seven long years, the three of you and the Dark Lady played a deadly game of cat-and-mouse. The three of you all lived, but a lot of your fellow students were collateral damage - you were so often just barely too slow to save them. Along teh way, too, you became close to \cGinny{}, \cRon{}'s twin \cGinny{\sibling}. The two of you dated for several years, and you had intended to marry \cGinny{\them} once everything was over.

Throughout your years at school, you and your friends entered into a bitter seven-years-long rivalry with \cMalfoy{}, the scion of one of the most prominent wizarding families, and his lackeys. \cMalfoy{}'s family was rumored to be in league with the Dark Lady's Endless, and your conflicts with \cMalfoy{} culminated in a duel during your sixth year, during which you nearly killed \cMalfoy{\them}. Later that year, when Headmaster Gaebora was killed by an Endless in order to claim the Paragon of Wisdom for Thevardra, everyone suspected \cMalfoy{} to be the murderer, although it was never proven.

And then came the fateful Battle of Katmeers. You knew, going in , that you were likely to die, as Headmaster Gaebora - Wielder of the Paragon of Wisdom - had died before you. You even knew that it was likey that your actions would unleash a deadly arcane backlash on your clasmates, but you couldn't warn them. Thevardra was a tactical master and surprise was your only hope; if there was any hint in your side's movements as to your plans, she would pick up on it and you would lose your chance of ever stopping her. You almost caved and warned \cGinny{}, but at the last minute you realized that you could not even do that, and you could only hope that \cGinny{\they} would be safe as you went to your final battle. You ran up to where Thevardra was just on teh verge of completing her ritual, and the two of you  dueled with your twin wands, locked in your own private world that gradually shrank down until all the intensity of your lifelong conflict existed in a singularity of wills at the point where the wands met. And drawing strength from the love of your friends and the memory of all who had died before, you pushed through. Everything snapped, the fabric of magic itself briefly tore, and wrapping your essence around Thevardra's writhing, wounded soul, you dragged her into the Shadow Realm, where the two of you were to trapped amongst the dead souls for all eternity.

Except that Thevardra was all too wily for you, again. Somehow as you dragged her to the Shadow, she managed to shed all of her ambition, and greed and anger from herself, leaving it behind her in the world. And most of her ample hatred as well, although she saved a little of it to torment you in the void. She's nothing if not vindictive. For the first many millennia you spent n the strange timelessness of the realms beyond, Thevardra would stop by regularly to taunt you about what you had let her leave behind, and what terrible evil it could continue to spread, even though the reign of the Endless Lady was now, effectively, ended. She told you it could make another as powerful as she had been, and in a much shorter time. In the end, all you had done was trade a Dark Lady for a probable Dark Lord. It was this more than anything else about the chaotic Shadow Realm that made it your own personal hell - knowing that somehow, you had failed yet again, and that even the sacrifice of your own life was not enough to save the world after all. Maybe Fate had made a mistake when it chose you.

It was almost cruel that you were offered another chance, and the means by which you were offered it were horrifying. \cHermione{} -- sweet \cHermione{}, your heroic best friend -- apparently was so lost without you that \cHermione{\they} turned to the near-forgotten Dark Art of Necromancy in order to drag your soul back to the realms of the living. But wors of all, although you live again, you can no longer do magic. Your ability to cast spells was apparently burnt out by the final confrontation with Thevardra during the Battle of Katmeers. You have a terrible failure to atone for, and you literally have no tools to begin to solve the problem. And you can't ask for help either, because if it is found out that you are alive again, people will find out about \cHermione{}'s crime and thee will literally be a \cHermione{\magician} hunt. Life in Lon-Lon is the best outcome for \cHermione{\them} from such an event, adn you don't like to think of the worst. even if you are a little afraid of how intense and reckless \cHermione{\they}'s become, you can't let that happen.

Feeling hopeless, you became consumed with depression, and avoided the wizarding world as much as you could. When you ahd to leave the house, you donned a ring of polymorph (your ``wedding'' ring) and posed as \cHermione{}'s Muggle husband, ``\cHarry{\MYname}'' but you did this as little as possible. You tend to spend a lot of time sitting around, drinking beer and trying to come up with some way to find and destroy the remnants of Thevardra without magic. When \cHermione{}'s 10-year reunion invitation came, you realized that this was a golden opportunity. One of your surviving classmates might have some leads on what became of the shard of Thevardra's Wrath. And it would not be too strange for \cHermione{} to bring \cHermione{\their} \cHarry{\spouse} with \cHermione{\them}, surely. You've managed to convince \cHermione{} to let you come, although \cHermione{\they} is not keen on the idea. perhaps truly at last you will be able to fulfill your purpose and purify the whole wizarding world.

\begin{itemz}[Goals]
	\item Find and destroy the shard of Thevardra.
	\item Protect \cHermione{}'s secret.
	\item Try to help your classmates rebuild their lives.
\end{itemz}

\begin{itemz}[Notes]
	\item The polymorph cast by your ring will fade within one minute if you remove it.
\end{itemz}

\begin{contacts}
	\contact{\cRon{}} One of your best friends. \cHermione{} sometimes calles \cRon{\them} a useless drunk, but you ahve a hard time imagining staunch, steadfast \cRon{} that way.
	\contact{\cGinny{}} Your \cGinny{\significant}, before your death. You feel like you betrayed \cGinny{\them} when you didn't warn \cGinny{\them} about the backlash, and don't know how to begin to atone.
	\contact{\cHermione{}} Your other best friend, now a necromancer. You often wish that \cHermione{\they} had left well enough alone, but htere is nothing to be done about that now. The terrible secret inevitably means that \cHermione{} is the only one you can fully trust, and vice versa.
	\contact{\cMalfoy{}} Man, you hate that \cMalfoy{\guy}. \cMalfoy{\They} was a prick to you for years for no good reason, and then trhew \cMalfoy{\their} lot in with the Endless. Also, you now know perfectly well that \cMalfoy{\they} killed Headmaster Gaebora. THevardra gloated about it for a few centuries before she got bored and moved on to other topics.
\end{contacts}

\end{document}