\documentclass[char]{Katmeers}
\begin{document}
\name{\cHermione{}}

\updatemacro{\cHarry}{
  \nickname{Drew Carpenter}
  \mapnickinformal
}

You are one of the greatest \cHermione{\magician}s of your time. Despite being born of two Muggle parents - for which you have faced discrimination since you entered the wizarding world as a child of ten - you have had considerable natural aptitude for magic, and you studied hard to improve your abilities even further. You have never met a spell you that you could not master.

Despite all the hell you went though in school, right up to the Battle of Katmeers, you would have said your life was pretty good. You had your best friends, \cRon{} and \cHarry{}, and you thought that there was nothing the three of you couldn't conquer, from monsters wandering the grounds of Katmeers all the way up to The Dark Lady Thevardra herself. You were the studious, thoughtful one, the one with the clever insights and actually thought-out plans. It was not for nothing that you were sorted into Lanayru. Your Faron friends used to to sometimes tease you about being an egghead and you used to tease them back about never ever looking before the leaped, but it was all in good fun. The three of you planned to become Aurors together, and chase down the Dark wizards, wherever they hid. You were especially close to \cRon{}; the two of you fell in love at some undefinable point in your time at Katmeers, and you agreed to marry \cRon{\them} after graduation.

But when \cHarry{} died at the Battle of Katmeers all your dreams turned to ash. You were standing nearby when it happened, and you tried to shield him with your Patronus charm, but you weren't strong enough to protect him. Your Pratonus shattered and Drew was vaporized right in font of you - and worse, all the others whom you had been protecting with your Patronus, now defenseless, were caught in the ensuing backlash. You were only saved because \cRon{} managed to throw up \cRon{\their} own Patronus in time to protect the two of you. The moment haunts you. If only you had been a little stronger, you could have saved \cHarry{} and all the rest, and you know it. \cRon{} knows it too, although he never speaks of it. But you can tell. The two of you still got married, but somehow, there was always a rift between you.

You became an Auror like you'd planned, although \cRon{} did not join you. \cRon{\They} joined the Ministry instead, and \cRon{\their} status in the Ministry rose at the same rapid rate as the drinking problem \cRon{\they} developed after the Battle of Katmeers. Meanwhile, you grew obsessed with trying to purge your guilt over \cHarry{}'s death by finding some way -- any way! -- that \cHarry{\they} could be brought back. You spent long hours poring through dusty libraries and archives searching for some way, some spell, and discovered that, if a person who embodied a perfect balance of the three virtues could recover the Paragons from wherever they had vanished to after the death of their previous wielders, that person would be granted one wish. You chased the Paragons around the world, often leaving home for weeks at a time. Sometimes you remembered to tell \cRon{} you were going, sometimes you didn't -- you had to hurry or the trails would go cold after all.

And at last you found them, the golden Paragons, with all their longed--for potential, shimmering in a forgotten temple full of traps and monsters. You touched them, but you were no longer in balance. The Paragons split, and two of them vanished, leaving you with the one you most embodied now.

Power.

You were mortified by this. It felt like the Paragons had just accused you of being Thevardra's heir. But so be it. You came home to an irate \cRon{}, who demanded that you leave off your preposterous quest and move on with your life -- not that \cRon{\they}'s managed to, of course, but \cRon{\they} likes to pretend \cRon{\they} has. You said you'd try, but you couldn't, not when you had come so close. \cRon{} ultimately divorced you. You haven't seen much of \cRon{\them} since, but you've become so preoccupied with your work you almost haven't had time to miss \cRon{\them}. Almost.

Searching for the other two Paragons proved a confusing and difficult task, but while you were studying arcana in a cache of forbidden knowledge (abusing your Auror privileges to do so) you discovered another, much faster way: necromancy. Like so many of the Dark Arts, it wasn't even that hard to do. Absconding with the tome, you set about conducting the ritual to pull \cHarry{} back. It worked, but even in this nothing turns out the way you want it. \cHarry{} lives again, but \cHarry{\they} can no longer do magic. \cHarry{\They} is moody and spends all of his time moping on your couch and drinking all your beer and seems to resent you for what you did. Meanwhile, you are depressed by this person who is no longer the \cHarry{} you knew, but the secret binds you together. You made \cHarry{\them} a charm of polymorph (\cHarry{\their} ``wedding ring''), and \cHarry{\they}'s been posing as your Muggle husband, \cHarry{\MYname}, on the rare occasions that \cHarry{\they} goes out at all. if you could find the other two Paragons, perhaps you could restore \cHarry{\their} abilities, but you fear that the other two Wielders, whoever they are, would know what you did, and you would quickly find yourself rotting in Lon-Lon. \cHarry{} was unusually interested in coming to this reunion, and \cHarry{\they} managed to get you to reluctantly agree to bring \cHarry{\them} along, citing \cHarry{\their} need to see his old friends again and to get out of the house.

\cHarry{} doesn't like to talk about what happened between \cHarry{\them} and Thevardra, but once in an unguarded moment, \cHarry{\they} mention something about a shard of her remaining in the world. Presumably not enough to cause the same horrors that Thevardra herself did, but still, perhaps, enough  to corrupt the unwary and drag them down a Dark path. You decided to set about finding it. As insurance, you also anonymously tipped off you fellow Aurors, although you suspect that you are in a much better position to deal with the problems than they are. Carefully, cautiously, you have snaked your way onto the radar of the Dark Wizards, posing as a power-hungry necromancer, trying to find your way back to their ringleader, who surely bears Thevardra's shard. The trail has led you to this reunion, whee there are hints that the new leader of the Endless will be present. If you can find him or her, you will be able to end Thevardra's influence over the world at last.

\begin{itemz}[Goals]
	\item Find and destroy the shard of Thevardra
	\item Bring the Dark wizards to justice
	\item Help \cHarry{} regain the ability to do magic
	\item Come to some sort of terms with \cRon{}
\end{itemz}

\begin{itemz}[Notes]
	\item Your ``\iRing{}'' is a backup polymorph charm for \cHarry{}.
\end{itemz}

\begin{contacts}
	\contact{\cRon{}} you often bitterly call \cRon{} a useless drunk, but you still deeply admire who \cRon{\they} used to bee. If only \cRon{\they} were still that person.
	\contact{\cNeville{}} Your fellow Auror, who is very good at \cNeville{\their}  job. \cNeville{} is thoughtful and brave, but \cNeville{\they} has trouble trusting anyone ever since \cNeville{\they} found out how many of your classmates were Endless, and that makes \cNeville{\them} dangerous.
	\contact{\cHarry{}} Things have been rather awkward between you and \cHarry{} since \cHarry{\their} revival. But \cHarry{} was very excited to come here tonight, and you hope that seeing everyone again will help \cHarry{\them} snap out of \cHarry{\their} depression.
\end{contacts}

\end{document}