\documentclass[char]{Katmeers}
\begin{document}
\name{\cLucius{}}

\updatemacro{\cHarry}{
  \nickname{Drew Carpenter}
  \mapnickinformal
}

You were once the beloved only \cLucius{\offspring} of the wealthiest and most influential family in the wiarding world. Your father was the Minister of Magic, your mother, a social force that everyone lived in awe and terror of. Everything you could ever desire was granted immediately by your doting parents. Like your parents before you, you were sorted into Eldin House. You had intended to be a leader of your House, but after the first few weeks, you could see how things were coalescing around \cMalfoy{}, and rather than be outcast, you grudgingly pretended to be his friend. You mostly spent your time around others of your house, eschewing the peasants of Faron of Lanayru. You were condescendingly fond of \cGhost{\formal} and \cGoyle{\formal}: although not great wizards, they had a certain low cunning that you could appreciate. You also, somewhat to your own surprise, were friends with \cCrabbe{}, whose discretion and wisdom made \cCrabbe{\them} a perfect confidant.

You really didn't pay much attention to everything going on with Thevardra and her followers for most of your time at school. YOu were too busy plotting to overthrow \cMalfoy{\formal} and take your rightful place at the top of Eldin's hierarchy. So it came as quite a shock when it was discovered that your parents had been Thevardra's puppets for years. You had no idea what to make of this. You didn't know what to do. Should you join Thevardra and the Endless, like so many of your house mates seemed to be doing? Or should you make the moral choice, and fight against her?

Well, you might be somewhat blinded by pride, but even you could see that if Thevardra succeeded in her quest for purity, it would destroy the wizarding world. You resolved to side against her. You were afraid to act against her directly, so you did what you could to quietly feed information to the resistance. Perhaps it wasn't much, but you hope that it made a difference. You didn't really fight in the final battle either - you were never much at combat. You regret that, sometimes.

After the battle, you fell into hell. Your parent's notorious crimes led the Aurors to suspect you of being allied with Thevardra as well, and you were arrested along with most of the rest of House Eldin. You were confident, however, that you would be acquitted when you went to trial. But then the unthinkable happened - the prosecution had hard evidence that all but proved your guilt. It must have been planted, but whoever did it knew what they were doing, and you were convicted and sentenced to life in Lon-Lon Prison.

You were there for three years before you finally won your appeal. Three years in that joyless, maddening place, surrounded by the most terrifying Dark wizards the world has ever seen. Your sanity was under constant assault, and the only thing that kept you from spiraling off into madness was your burning anger over your betrayal. You compiled a lengthy list of all the people that it could have been. You pored over the scraps of evidence again and again. You vowed revenge against whoever it was. It has become your most important mission to find your transgressor, and make them understand a fraction of what you endured.

Adding insult to injury, you are now broke. The \cLucius{\formal}s used to be extremely wealthy, but when you were finally released from Lon-Lon and went to withdraw some funds from the family vault at Gringotts, you discovered that the vault was all empty. It might have been theft, but the Ministry confiscated the assets of a lot of Dark wizards in the aftermath of the war, and you are worried that lodging a protest could end up stirring up bad blood and making you powerful enemies that you cannot afford to have.

The pursuit of justice is a slow endeavor, and you were not so obsessed that you didn't realize that you also needed to rebuild the shards of your life. It was a long, difficult process, since despite the overturning of your conviction, many people were still suspicious of you. And all the things that were supposed to skyrocket yo to the pinnacle of the wizarding world - your parents, your friends in House Eldin - all of them counted against you now. But you persevered, and managed to worm your way into the Ministry, and then even managed to become the chief aid to \cRon{}, your former classmate and the current Minister of Magic. \cRon{} is a useless drunk these days, and you are the power behind the throne. The hardest part of your job is keeping the Minister from saying things that will sink \cRon{\their} political career, since you have hitched yourself to it as your last hope. It stings your pride that you have to hide behind some uncouth Faron lout, but for now, it must do.

Unlike most everyone else here, you actually do want to attend this reunion. It's a great opportunity to network, and  also, you are certain that your transgressor was one of your classmates. it's a good opportunity to get some detective work done.

\begin{itemz}[Goals]
	\item Find out who betrayed you, and get revenge.
	\item Keep Dirk out of trouble. Find a way to spin any indiscretions he might commit.
	\item Network with your former classmates and try to improve your relationships with them.
\end{itemz}

\begin{itemz}[Notes]
	\item You sort of picked up \aAK{} in Lon-Lon.
\end{itemz}

\begin{contacts}
	\contact{\cRon{}}  A worthless drunk, but \cRon{\their} useful to you as a figurehead for now. You haven't ruled him out as a suspect though. The \cRon{\formal}s never had any money, and it's hard to get anywhere in politics without funding from somewhere, such as liberating it from the vault of a disgraced rival family.
	\contact{\cNeville{}} \cNeville{} has grown deeply paranoid since discovering how many of \cNeville{\their} erstwhile followers were actually working for Thevardra. Paranoid enough th decide you were guilty and then fabricate the evidence to support it? You're not sure.
	\contact{\cGinny{}} \cGinny{} was rumored to be an accomplished thief, and again, the \cGinny{\formal}s were never wealthy.
	\contact{\cHermione{}} No one would suspect an Auror of such a thing, and that seems to you the perfect alibi for almost any crime. \cHermione{} just acts like \cHermione{\they}'s got something to hide. And \cHermione{\they} never liked you.
	\contact{\cLuna{}} Okay, it does seem unlikely that it was \cLuna{}. There isn't a devious bone in \cLuna{\them}.
	\contact{\cCrabbe{}} in many ways \cCrabbe{} was your only real friend, and the only one who cared about you as a person. \cCrabbe{\They} also never took much interest in worldly affairs - most of his time was spent tending to the ghosts. It doesn't seem very likely that it was \cCrabbe{\them}, either.
	\contact{\cMalfoy{}} You had a long, quiet rivalry with \cMalfoy{\formal}, each of you trying to establish dominance over House Eldin, and by extention, Katmeers. \cMalfoy{\They} is your prime suspect, especially since those kind of underhanded tactics seem particularly favored by \cMalfoy{\their} family.
	\contact{\cGoyle{}} \cMalfoy{}'s lackey, and occasionally yours as well. You wouldn't have thought \cGoyle{\them} smart enough, but toward the end of your time at Katmeers, you started to realize that \cGoyle{\they} was a lot more clever than \cGoyle{\they} let on.
\end{contacts}

\end{document}