\documentclass[char]{Katmeers}
\begin{document}
\name{\cLuna{}}

\updatemacro{\cHarry}{
  \nickname{Drew Carpenter}
  \mapnickinformal
}

You are the only child of the wizarding world's foremost authority on Muggles. This is a somewhat dubious distinction, of course, as most wizards oculd not care less about Muggles, but it's important work and you were always very proud of your father. You shared his interests, but in truth you were really just curious about all the untold things in the world, including or perhaps most especially the things that everyone else thought were fictional of beneath their notice. Many of your classmates considered you spacey and eccentric, but you never really minded. You were sorted into Lanayru, where people tended to be more sympathetic to your oddities.

Throughout the fight against Thevardra, you lent your expertise to the cause. \cHarry{} and \cHarry{\their} friends came to value your judgment, and you'll admit that it was nice, being appreciated for once. You weren't the researcher that \cHermione{} was, but you knew more about things like Muggles, and ghosts, and myths and rumors. You fought alongside everyone else at the final battle, and you are proud to say that your efforts made a difference. It was so sad about all of your friends, though. Especially \cHarry{}. You miss \cHarry{} a lot; the wizarding world is not the same without \cHarry{\them}.

Which is why, after graduation, you left. Not wanting to think about the sad, sad fate of your friends, you went to explore the world as your fancy took you. For the first few years, you were interested in herbalism and archeology. You traveled all over the world searching for rare herbs and interesting artifacts. You visited eldritch forests and ancient deserts and forgotten temples, and found many strange and wonderful things. There are too many of these to list them all, but one of the most curious was a large crystal. It was scintillating and beautiful, but underneath the surfaces you could see dark eddies of something that moved almost as if it were alive. You have no idea what it could be. You found it near a desiccated skeleton, but as this was in the desert, that doesn't really tell you much. There are a lot of dessicated skeletons in the western desert. Nonetheless you like having it around, it's just so cool.

But eventually you had your fill of desolation. You tried returning too the wizarding world, but it only reminded you again of all your friends who had died or gone insane or been sent to Lon-Lon. Depressed, you wandered again, this time to the strange world of the Muggles. You spent a few years living amongst them, studying their peculiar ways - your father would be so proud. And you had a revelation as you became more familiar with them. It is pure folly for the wizarding world and the Muggle world to separate themselves, especially as the Muggle technology has made them capable of feats that are practically like magic.

The more you thought about it, the more you realized the wisdom of this. After all, Thevardra was an advocate of keeping the worlds apart - clearly then the only course is to erase those boundaries, tear down the Veil, and bring the worlds together. It would revitalize the often-stagnant wizarding world, and of course there is so much the wizards, with their superior understanding of the truth of the world, could do for the Muggles. You have tried to spread your doctrine to other wizards, but most of them have been rather resistant to the notion. They fear that the Muggles would reject the wizards and fear them as tyrants. ``mobs with pitchforks,'' everyone keeps saying. ``Paranoid trials and bonfires.'' Nonsense. The Muggles are much more progressive than that now. Only good could come of this.

Unexpectedly, one of your few allies came in the form of \cMalfoy{}, who has changed drastically since \cMalfoy{\their} days as the unofficial \cMalfoy{\King} of house Eldin. \cMalfoy{\They}, too, spent time living amongst the Muggles, and \cMalfoy{\they} agrees that it is time to tear the barriers down. So the two of you have come to the reunion tonight. There are many amonst your classmates who have considerable influence, and maybe they can help you. \cMalfoy{} suggested that you draft a petition and try to get \cRon{}, the Minster of Magic, to sign it, if \cRon{\they} comes. The petition would call for the immediate end of the ridiculous masquerade and the integration of the two halves of the world; surely the Minister of Magic's signature would be enough to accomplish your goal.

\begin{itemz}[Goals]
	\item Get \cRon{} to sign your petition to dissolve the Veil.
	\item Recruit your classmates to your cause.
	\item Keep ahold of the mysterious crystal and protect it. It's too fascinating to let anything bad happen to it. Perhaps its power could aid in your cause.
	\item Find a way to permanently make Muggles equal with wizards.
\end{itemz}

\begin{itemz}[Notes]
	\item Do NOT open the \iCrystal{} item-card. This applies only to characters other than you.
	\item If you relinquish control of \iCrystal{} for any length of time, alert a GM immediately.
\end{itemz}

\begin{contacts}
	\contact{\cHermione{}} Your fellow Lanayru, and \cHarry{}'s right hand researcher. You have a bit of a friendly rivalry with \cHermione{\them}, since both of you are interested in arcane esoterica, but \cHermione{\they} tends to be much more methodical about it than you, and thus misses half the exciting stuff. You respect \cHermione{\them}, but you think \cHermione{\they} needs to be less closed-minded.
	\contact{\cCrabbe{}} Even before \cHarry{} took you into \cHarry{\their} trust and believed your intuitive understanding of the world, \cCrabbe{} did.  Perhaps it was because \cCrabbe{\they}, too, could see things no one else could. You've always gotten along well with \cCrabbe{\them}.
	\contact{\cMalfoy{}} \cMalfoy{} used to be pretty unlikable, but \cMalfoy{\they}'s mellowed out over the years, and now \cMalfoy{\they}'s your closest ally in your quest to unite the two worlds.
	\contact{\cHarry{\MYname}} A Muggle! \cHarry{\they} would be the perfect ally in your quest - surely \cHarry{} they already knows that the Veil is a pointless anachronism!
	\contact{\cFairy{}} A fairy! You know very little about them, but you have always been fascinated.
\end{contacts}

\end{document}