\documentclass[char]{Katmeers}
\begin{document}
\name{\cMalfoy{}}

\updatemacro{\cHarry}{
  \nickname{Drew Carpenter}
  \mapnickinformal
}

When you think back on who you were at Katmeers, you just have to shake your head in abject shame. You were the scion of one of the oldest and purest Houses of the wizarding world, and both your parents were extremely prominent and powerful within the community. The power went to your head. You were an unholy terror from day one of school, the ringleader of a band of fellow arrogant elitists - most especially \cGoyle{}, \cCrabbe{} and \cLucius{} - and you quickly developed a vicious rivalry with \cHarry{} and \cHarry{\their} friends. This was occasionally quite violent - one time you dueled \cHarry{} and you lost; you could have died, except that you had a bottled fairy your father gave you, and \cFairy{\they} pulled you back from the brink. When you arrived at Katmeers, you were sorted into Eldin, and you were intensely proud of that. You were not particularly brave or studious, but charisma and a certain low cunning got you far within the petty hierarchy of school.

As Thevardra's power grew, however, your world began to unravel. Your parents showed their true colors as members of the Endless, and you were dragged into it somewhat reluctantly - you had no interest in exposing yourself to that kind of danger, no matter what the reward. Thevardra found you a useful tool to attack \cHarry{}, and ultimately you were made into her pawn, through threats of dire tortures to be visited, not on you, but on your parents and your friends, whom you were genuinely fond of in a kind of condescending way. You quickly came to resent the Dark Lady deeply, but were forced to commit several terrible crimes in her name, including killing the Headmaster of Katmeers to attain the \iWisdom{} for Thevardra.

To your great shame, you did very little in the final battle. Afraid to be found fighting on the losing side, you mostly stood, there paralyzed by uncertainty and fear. Your friends looked to you for which way they should turn, and you had no answers. While you dithered, a stray curse shattered the balcony from which you were watching the battle to make a decision, and \cGhost{\formal} fell to \cGhost{\their} death. If only you could have made up your mind earlier. You were so shocked you barely noticed when \cHarry{} and Thevardra had annihilated each other and the battle was ended.

In the aftermath, your parents and so, so many of your friends were sent to Lon-Lon prison. You managed to plead that all you had done you had done under duress, and you were acquitted in court, but the angry mob outside the court room was not mollified. You fled the wizarding world and found yourself in the suddenly in the strange realm of the Muggles whom you had always so despised. You moved to Kakariko City and tried to blend in. And gradually, at first out of necessity and then out of penitent curiosity, you began to try to understand them, these unfortunate souls who were born with no concept that magic even existed. You lived in one of their little apartments, read their oddly lifeless books, and sought out their wisest to teach you to understand what life without magic could mean.

And finally, in an ashram high in the mountains, enlightenment gradually coalesced from all you had seen. You had been wrong all along. The worth of a man was not measured by his magical potential, but by his actions - and you had behaved abominably all your life. And instead of trying to flee from this wrenching realization like you had always fled from everything unpleasant in the past, you decided to face everything you had done, and try to do whatever you could to make amends. The terrible way you had treated your friends? You would treat them better now. The years of bullying and belittling you had heaped on your classmates? you would show them the respect and support that the had always been due. The crimes that you had committed under Thevardra's commands? You had still done them out of your own weak cowardice, and you must find some way to atone. You knew it would be a hard and terrible task, one that might take the rest of your life, one that might even be impossible, but you have entirely devoted yourself to it. 

At the very moment you formally made this resolution, a shining golden meteor descended from the heavens. It was the \iCourage{} and it had chosen you as it's Wielder. You were awed - you felt that there must be some mistake - but humbly accepted the charge. On your return to the wizarding world, you have told no one that you have it - there would be outrage if it were known that such a dubious character as yourself held such a sacred artifact.

As you knew would be the case, almost no one will talk to you, and your quest for redemption as been very slow. But there has been one happy surprise - \cLuna{} heard what you were doing and reached out to you. You used to consider \cLuna{\them} pathetic at best and dangerously insane at worst, but you now can see the wisdom that underlies \cLuna{\their} eccentricity. \cLuna{} explained to you that \cLuna{\they} is hoping to modernize the magical world, and tear down the false barriers that exist between wizards and Muggles. you agree with \cLuna{\them} entirely, and the two of you have become unlikely allies in this endeavor. \cLuna{} drew up a petition calling for the immediate dissolution of the Veil, but very few people seemed interested in signing it; you pointed out that if the two of you could convince \cRon{} to sign the petition, \cRon{\they} could use \cRon{\their} powers as Minister of Magic to bring it into effect almost immediately.

It also occurs to you that, if you could unite your Paragon with the other two (\iWisdom{} and \iPower{}), you could use the wish in order to fully blend the two worlds by granting all Muggles the ability to cast magic. You are certain that the Wielder of \iWisdom{}, whoever he or she is, will see that this is the best course; on the other hand, you have some concerns about whoever inherited Thevardra's former piece: \iPower{}.

You are here tonight to help \cLuna{}, and also in hopes of reconciling with your classmates. You hope they'll be willing to speak with you. You haven't seen many of them since graduation, and you did not part on the best of terms. But time heals many wounds, and you are very hopeful.

\begin{itemz}[Goals]
	\item Reconcile with your classmates.
	\item Convince \cRon{} to sign \cLuna{}'s petition.
	\item Keep the \iCourage{} safe.
	\item Unite the Paragons and use your wish to grant the ability to cast magic to the Muggles.
\end{itemz}

\begin{itemz}[Notes]
	\item Thevardra taught you \aAK{} back when you were her pawn.
\end{itemz}

\begin{contacts}
	\contact{\cLuna{}} A true open mind, \cLuna{} is the only one who is willing to be reconciled with you, and your partner in trying to end the pointless charade of the Veil.
	\contact{\cLucius{}} One of your old school buddies. You weren't as close t \cLucius{\them} as you were to \cGoyle{\formal} and poor \cGhost{\formal}, but the two of you were always on good terms.
	\contact{\cGoyle{}} Your loyal friend throughout your time at Katmeers. You were genuinely fond of \cGoyle{\them}, but never really did right by \cGoyle{\them}.
	\contact{\cHarry{\MYname}} You've never met \cHarry{\them} before, but a Muggle who already can pierce the Veil is likely to be a valuable ally in your and \cLuna{}'s quest.
	\contact{\cFairy{}} Your family had a fairy in a bottle once. While it almost certainly wasn't \cFairy{\them}, you feel like you should try to make it up to \cFairy{\them} as a proxy.
\end{contacts}

\end{document}