\documentclass[char]{Katmeers}
\begin{document}
\name{\cNeville{}}

\updatemacro{\cHarry}{
  \nickname{Drew Carpenter}
  \mapnickinformal
}

You're not a great \cNeville{\magician}. You admit it. Although both of your murdered parents were great Aurors, you weren't born with a lot of aptitude for magic. Nonetheless, you've managed to take what you have and do the most with what you could. When you first arrived at Katmeers it was nastily rumored that you were practically one of those sad wizarding children born without magic, but you proved simply to be a late-bloomer, gradually catching up with the rest of your classmates in the latter half of your Katmeers career.

In the final year of school, while your friends \cHarry{}, \cHermione{}, and \cRon{} were off trying to collect the Paragons before Thevardra could, you were back at Katmeers, holding down the fort. You and \cGinny{} rallied the other students around you, helping them cope with all that was happening and leading them against the forces of darkness in several skirmishes throughout that year. Unlike \cHarry{}, though, you tended to martial your forces very carefully; your relatively lesser magical talents have taught you that wielding a lot of power is often not as effective as the clever application of a small amount of force. You were instrumental in the Battle of Katmeers, heroically holding the line so that the bulk of Thevardra's forces could not reach her before \cHarry{} destroyed her. You saw a great many friends die that day, but you understand that their sacrifice was necessary. You mourn them, but unlike many of your classmates, their loss has not dominated your life.

When you discovered how many of your classmates were secretly working for Thevardra, you were appalled. As you had come to be the acting leader of the student body, it felt like a personal betrayal. If these people whom you had known so well could turn out to be Dark Wizards, then literally anyone might be. You felt you could never trust anyone again, and you swore that you would hunt down all of Thevardra's remaining followers and bring them to justice, making sure that none of them would be in a position to cause destruction ever again. You became an Auror shortly after graduation, and have predominantly been assigned to do field work ever since.

Your travels have taken you to a lot of strange places, where you have acquired a number of strange things, most of which are useful devices that you channel magic through, which helps you compensate for your lesser magical capabilities.  You also have acquired a companion. While in an ancient and eldritch forest, you encountered the fairy \cFairy{}, who has attached \cFairy{\their}self to you, unbidden, to your cause. the poor thing appears to be extremely simple, but \cFairy{\they} clearly means well. You are grateful for \cFairy{\their} magical aid, although you often find \cFairy{\their} conversation somewhat tedious. But it would be impossible for \cFairy{} to be a Dark wizard, being not a wizard at all, and having one trustworthy ally has been comforting.

A curious thing happened a few years back. You and \cFairy{} were tracking one of Thevardra's followers through a shifting desert, and on the steps of a long-forgotten temple, you paused, and saw a shining meteor streak from the sky. It flew into the uppermost chamber of the crumbling ruin, and you went to investigate. You battled your way through the forgotten horrors that dwelled within the temples, destroying dark idles and breaking many pots as you went. The uppermost chamber was home to a hideous bon sphinx that you had to defeat in a deadly game of riddles, bot once it had been destroyed, you were surprised to find that the shining meteor was in fact the Paragon of Wisdom, which had chosen you as it's wielder. You are honored, of course - you had always tried to embody justice, balance, and clever thought, but you would have expected the honor of carrying this Paragon would go to a Lanayru.

\cFairy{} told you, in he repetitive, but occasionally informative way, that finding one of the Paragons alone could only mean one thing: someone else, who did not have all three virtues in balance, must have found all three paragons in their hiding place, presumably meaning to use them to make a world-changing wish. Upon contact with such a person, the Paragons split. That person would be left with the shard that most aligned with them, while the other two would find new, suitable wielders. The news concerns you - who attempted to use the Paragons, and what did they hope to accomplish, and which virtue did they embody? There's a fifty-fifty chance that it was Power, after all, and you are all too aware that the previous wielder of the Paragon of  Power was the Dark Lady herself. If Thevardra's forces are stirring yet again, then no one can be trusted. You have elected to keep your new charge to yourself, for now.

Reinforcing your concern, two things have come down to you from the Auror's Office: first, someone stole a tome of necromancy - one of the Dark Arts - from a highly secured archive. You hate to think this, but back in the day, \cGinny{} was frighteningly good at getting in and out of places that one one should have been able to access. Also, and much more worrisome, the Aurors recently received an anonymous tip that a shard of Thevardra's soul may still remain in the world. Not enough to cause the same horrors that Thevardra herself did, but still, enough to corrupt the unwary and drag them down a Dark path. You have been tasked with finding the shard and destroying it, and hopefully ridding the world of Thevardra forever. This is what brings you here tonight. You thought you'd managed to hunt down all of hte Endless amongst your classmates, but you still have doubts about several of them - everyone knows that \cMalfoy{}'s parents were both Endless, and \cLucius{} was actually convicted of being one of Thevardra's followers, although \cLucius{\they} was later let out of Lon-Lon on appeal, under somewhat dubious circumstances.

\begin{itemz}[Goals]
	\item Find and destroy the shard of Thevardra.
	\item Bring all Dark wizards to justice.
	\item Find the Wielders of \iPower{} and \iCourage{}, and determine their intentions.
\end{itemz}

\begin{itemz}[Notes]
	\item You have a number of abilities that require certain items to perform. With the exception of \aDekuStun{}, using the abilities does not consume the item.
\end{itemz}

\begin{contacts}
	\contact{\cGinny{}} Your good friend and partner in rallying the students that last year at Katmeers. \cGinny{\they} embodied Faron courage, and you admire \cGinny{\them} a lot. You haven't really spoken to \cGinny{\them} in years, though.
	\contact{\cHermione{}} Your fellow Auror. \cHermione{\They} spends a lot of time off on special assignment, which makes sense, since \cHermione{\their} particular area of expertise is research.
	\contact{\cMalfoy{}} \cMalfoy{\formal} picked on you mercilessly all throughout your time at Katmeers, which already disposes you ill towards \cMalfoy{\them}. Then \cMalfoy{\they} turned out to be allied with the Endless (no matter what the court decided), and probably also killed Headmaster Gaebora. One of your least favorite people.
	\contact{\cLucius{}} Kind of an elitist snob. Also, \cLucius{} was convicted of being Endless, and you find the circumstances of \cLucius{\their} subsequent appeal dubious. The \cLucius{\formal}s had a lot of wealth, and then shortly after \cLucius{} was let out of Lon-Lon, it was discovered that all of it had mysteriously been spent. How could anything be more obvious?
	\contact{\cFairy{}} Your fairy companion. \cFairy{\they}'s a little clingy, but honestly, \cFairy{\they}'s the only one you can trust.
\end{contacts}

\end{document}