\documentclass[char]{Katmeers}
\begin{document}
\name{\cRon{}}

\updatemacro{\cHarry}{
  \nickname{Drew Carpenter}
  \mapnickinformal
}

Unlike your friends \cHermione{} and \cHarry{}, you're a pretty ordinary guy, except for being a \cRon{\magician}. \cHermione{} is brilliant and \cHarry{} was touched by fate, but you're just a middle child - one of a pair of twins, with your \cGinny{\sibling} \cGinny{} - of a large but not terribly important wizard family. You're not a bad \cRon{\magician}, but not a great \cRon{\magician}. Just a guy,basically, who is also a \cRon{\magician}.

Despite all the hell you went through in school, right up to the Battle of Katmeers, you would have said that your life was pretty good. You ahd your best friends, \cHermione{} and \cHarry{}, and you thought that there was nothing the three of you couldn't conquer, from monsters wandering the grounds of Katmeers all the way up to the Dark Lady Thevardra herself. YOu had every faith that \cHarry{} could and would defeat the Endless, and you set yourself to do everything you could to help \cHarry{\them} to that end. And of course, there was \cHermione{}. Beautiful, brilliant, perfect \cHermione{} was the only \cHermione{\kid} that you could ever imagine being with. And miracle of miracles, \cHermione{\they} returned your affection. You proposed to \cHermione{\them} senior year, and \cHermione{\they} accepted. You intended to get married after graduation, and then become Aurors together with \cHarry{}, and chase down the Dark wizards, wherever they hid.

The Battle of Katmeers was a nightmare. You still have dreams about it almost every night. Your classmates dying around you, those who didn't turn against you and fight on the Dark Lady's side. And then cowering under \cHermione{}'s Patronus, and the terrible moment you saw it shatter, and \cHarry{}\ldots{} oh goddesses, poor \cHarry{}. You drink to forget the moment you watched \cHarry{\they} and the Dark Lady annihilate each other. Well, you drink to forget all of it, but especially that moment.

You didn't end up becoming an Auror after all. It seemed sort of pointless, after Thevardra's defeat, and you were tired of constantly living in fear of your life. Instead, you went to work in the Minstry of Magic. You've risen all the way up, and last year you were appointed the Minster. It'd be great if it didn't all feel so empty -- \cHarry{} really should have been the one in this job, not you. You try to act the way you know he would have, but it's hard, and you don't really know what you're doing. You let your press secretary, \cLucius{}, handle most things; as the \cLucius{\offspring}  of a former minister, \cLucius{\they} has intimate understanding of what is needed in every situation. Sometimes it occurs to you that it is odd that you have come to rely on someone whom you once would have described as a bitter enemy, but you suppose being able to forgive such silly,juvenile, quarrels is the mark of maturity.

Meanwhile, your marriage with \cHermione{}\ldots{} \cHermione{} became obsessed with what had happened to \cHarry{}. \cHermione{\They} became distant and broody, spending all of \cHermione{\their} time in archives and libraries trying to find some way to ``bring him back.'' You tried to dissuade \cHermione{\them} -- necromancy is one of the darkest of the Dark Arts -- but \cHermione{\they} just kept at it. \cHermione{\They} would be away for weeks at a time, sometimes without even telling you \cHermione{\they} was going. One time \cHermione{\they} came home after an especially long trip, and literally didn't leave \cHermione{\their} office for three weeks. Eventually, even you had to admit it was not a functional marriage, and you ended up getting a divorce. You haven't seen \cHermione{\them} since. Apparently \cHermione{\they} is married to a Muggle now? You guess it makes sense, \cHermione{\their} parents were both Muggles, but still, it stings.

Although your duties as Minister, and your frequent dates with a bottle pretty much fill up your time, you've become aware that something is not quite right with your \cGinny{\sibling}, \cGinny{}. \cGinny{\They} seems distracted and distraught a lot of the time. Farore knows you're not exactly a fountain of comfort and cheer yourself, but you feel like you should try to reach out to \cGinny{\them} -- \cGinny{\they} is, after all,  your favorite \cGinny{\sibling}.

You don't really know what you're doing here. You've been wandering lost since your marriage fell apart, and to be honest, probably since \cHarry{}'s death. \cLucius{} said it would be good for you to attend the reunion, so you came.  At the least, maybe \cHermione{} will be there and you cna get some kind of closure with \cHermione{\them}, or maybe you can unravel what is troubling \cGinny{}. There's also an open bar, and that alone might make this worthwhile.


\begin{itemz}[Goals]
	\item Get closure with \cHermione{}
	\item Find out what is troubling \cGinny{} and see if you can help.
	\item Be a bold Minister of Magic who would make \cHarry{} proud.
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	\contact{\cGinny{}} Your twin \cGinny{\sibling} and your favorite sibling. \cGinny{\They} used t obe perky and optimistic, but hasn't really been the same since \cHarry{} died.
	\contact{\cHermione{}} Your estranged ex-\cHermione{\spouse}. You miss \cHermione{\them}. Or perhaps you only miss what \cHermione{\they} used to be?
	\contact{\cMalfoy{}} \cHarry{}'s old arch-nemesis, who also constantly reminded you that \cMalfoy{\their} family was more important than yours.
	\contact{\cLucius{}} Your press secretary, whom you rely on completely. Your administration would fall apart without \cLucius{\their} expertise.
	\contact{\cHarry{\MYname}} \cHermione{}'s new \cHarry{\spouse}. You've never met \cHarry{\them} before, but you hate \cHarry{\them} already.
\end{contacts}

\end{document}