\documentclass[blue]{Katmeers}
\begin{document}
\name{\bConcordance{}}

\updatemacro{\cHarry}{
  \nickname{Drew Carpenter}
  \mapnickinformal
}

\section*{Dramatis Personae:}

\subsection*{House Faron}

\hangindent=0.7cm {\bf \cRon{\intro}:} A close friend of \cHarry{}'s back in school, \cRon{} was always at the heart of all of \cHarry{}'s plans to thwart Thevardra.  After graduation \cRon{\they} entered the Ministry of Magic, and has risen all the way up to being the current Minister.  \cRon{} was married to \cHermione{\intro}, but they have since divorced.

\noindent \hangindent=0.7cm {\bf \cGinny{\intro}:} \cRon{}'s twin \cGinny{\sibling} \cGinny{} was one of the two students that the school rallied around the final year at Katmeers, while \cHarry{}, \cRon{}, and \cHermione{} were out searching for the Paragons.  \cGinny{\They} was clever and resourceful; there were a lot of rumors that \cGinny{\they} was also somewhat mischievous and an accomplished thief.  \cGinny{} was dating \cHarry{} for a few years before the end, and there were even rumors that they had been engaged.  \cGinny{\They} has been rather reclusive since the final battle.

\noindent \hangindent=0.7cm {\bf \cNeville{\intro}:} The other student who rallied the student body during the last terrible year, \cNeville{} was a dauntless and charismatic leader, which came as a bit of a surprise as \cNeville{\they} was gawky and foolish when \cNeville{\they} first arrived at Katmeers as a child.  \cNeville{} became an Auror after graduation, and is personally responsible for sending many Dark Wizards to Lon-Lon, including many of your corrupted classmates from House Eldin.

\subsection*{House Lanayru}

\hangindent=0.7cm {\bf \cHermione{\intro}:} Another very close friend of \cHarry{}'s back in school, \cHermione{} was the level-headed, knowledgeable one, the one who came up with all the workable plans and did all the research.  \cHermione{} became an Auror after graduation, but tends to work less high-profile cases than \cNeville{}.  \cHermione{} was married to \cRon{}, but they have since divorced; shortly thereafter \cHermione{\they} married the Muggle \cHarry{\MYname} in a secret ceremony - a scandal that rocked the wizarding world when it was discovered!  The couple has been very private ever since.

\noindent \hangindent=0.7cm {\bf \cLuna{\intro}:} \cLuna{} was always rather eccentric, constantly fascinated by odd things like Muggles and chasing after figments of legends that might or might not exist.  Although not always 100\% reliable, \cLuna{\their} vast collection of superstitions and trivia turned out to contain many vital clues that led to the defeat of the Endless Queen.  In recent years, \cLuna{\they} has emerged as a vocal advocate of Muggle rights.

\noindent \hangindent=0.7cm {\bf \cCrabbe{\intro}:} Even as a student at Katmeers, everyone would have described \cCrabbe{} as warm and wise.  \cCrabbe{\They} got along with everyone, even the Eldin crowd who tended to stick to themselves.  \cCrabbe{} had a particular aptitude for seeing hidden things and was blessed with the ability to see ghosts, who were invaluable spies in the fight against Thevardra.  \cCrabbe{\They} continues to study ghosts to this day.

\subsection*{House Eldin}

\hangindent=0.7cm {\bf \cMalfoy{\intro}:} The scion of one of the most prominent wizarding families, \cMalfoy{\formal} was the ringleader of the House Eldin crowd, perhaps to the chagrin of \cLucius{}.  \cMalfoy{\They} and his two cronies, \cGhost{\formal} and \cGoyle{\formal}, had a bitter, seven-year rivalry with \cHarry{}, \cRon{}, and \cHermione{}, which ranged from snide remarks to occasional outbreaks of minor violence, including a duel between \cMalfoy{\formal} and \cHarry{} that nearly left the former dead.  \cMalfoy{\formal}'s parents were both Endless and it was rumored that \cMalfoy{\they} was too.  \cMalfoy{\They} fled the wizarding world after the Battle of Katmeers and has only recently resurfaced.

\noindent \hangindent=0.7cm {\bf \cLucius{\intro}:} The other major social force within House Eldin was \cLucius{}, who was the son of Salman \cLucius{\formal}, the Minister of Magic during the Dark Times.  \cLucius{\formal} parents colluded with Thevardra, and in the investigation following the defeat of the Endless \cLucius{\they}, too, was convicted of being part of the conspiracy.  \cLucius{\They} was let out of Lon-Lon a few years later, and embarked upon a career in the Ministry, but an aura of suspicion still clings to \cLucius{\them}.  \cLucius{\They} is now Minister \cRon{\formal}'s press secretary.

\noindent \hangindent=0.7cm {\bf \cGoyle{\intro}:} \cMalfoy{\formal}'s only surviving henchman - \cGhost{\formal} died at the Battle of Katmeers when the balcony \cGhost{\they} was standing on shattered.  \cGoyle{\formal} was loyal and brave but not terribly bright, and has not particularly distinguished \cGoyle{\their}self after graduation.

\subsection*{Additional attendees}

\noindent \hangindent=0.7cm {\bf \cHarry{\MYname}:} \cHermione{}'s Muggle \cHarry{\spouse}, whom \cHermione{\they} married in a secret ceremony that was the talk of the wizarding world.  The couple has avoided public attention ever since.

\noindent \hangindent=0.7cm {\bf \cFairy{\intro}:} A fairy, companion to \cNeville{}, whom \cNeville{\they} met in \cNeville{\their} many journeys post-graduation.


\section*{Glossary:}

\subsubsection*{The Paragons:} The Paragons are three sacred artifacts of great power, each representing one of the Three Goddesses who created the world (Farore, Din, and Nayru).  When united, they grant the one who united them a single, world-altering wish.  They were crucial to Thevardra's plans; she was only stopped because she was unable to unite them before \cHarry{} killed her.  The current whereabouts of the Paragons are unknown; they vanished in a flash of light during the final battle against Thevardra and have not been seen since.  The Paragons also each correspond to one of the Virtues - Wisdom, Power, and Courage - and they tend to seek out Wielders who embody their principle.  During the Dark Times, they were wielded by Headmaster Gaebora, Lady Thevardra, and \cHarry{}, respectively.

\subsubsection*{Lady Thevardra Lefours, the Dark Lady, the Endless Queen:} A Dark wizard of the worst kind, Lady Thevardra was the terror of the wizarding world for most of your pre-adult lives.  She sought immortality and omnipotence, to rule over the entire world and purify it of all those who were unworthy, which included all of the Muggles and all of you who were not members of the old wizarding families, or not good at magic, or otherwise defective in any way.  She was defeated shortly before you began your time at Katmeers by \cHarry{}, but her followers resurrected her. She nearly succeeded in carrying out her plans before she was again finally defeated in single combat by \cHarry{}, at the cost of \cHarry{\their} own life.  Thevardra was the wielder of the Paragon of Power.

\subsubsection*{Drew Carpenter:} A young and powerful \cHarry{\magician}, and one of your classmates, who courageously battled and defeated Endless Thevardra twice, ultimately sacrificing \cHarry{\their} own life in order to finally thwart her plans and save the wizarding world from her dark designs.  \cHarry{} was the wielder of the Paragon of Courage.

\subsubsection*{Headmaster Gaebora:} Old and wise, the beloved Headmaster of Katmeers was considered one of the very greatest wizards of this age.  Nonetheless, he was approachable by any of the students, and had a bit of advice, a cryptic hint, and a wry quip for any student who needed it.  He was murdered at the end of your sixth year; rumor has it that \cMalfoy{\intro} was the perpetrator but it was never proven.  Headmaster Gaebora was the Wielder of the Paragon of Wisdom.

\subsubsection*{The Endless:} One of Thevardra's titles, and also the colloquial name for her followers, who sought immortality at Thevardra's hands.  The Endless were a collection of the most vicious and depraved Dark wizards of the age, but those who were not hunted down and slain are now safely locked in Lon-Lon Prison and will remain there for the rest of their lives.

\subsubsection*{Lon-Lon Prison:} The most secure wizarding prison in the world, situated in the middle of a raging river.  It is said that the strange entities who guard Lon-Lon come from the Shadow Realm; they feed on despair and their touch destroys the ability to feel joy.  It is certain that most who are sent up the river quickly spiral into madness.

\subsubsection*{The Houses of Katmeers:} The students at Katmeers are organized into three houses, one for each of the virtues.  House Faron is associated with Courage; its colors are green and gold.  House Lanayru is associated with Wisdom; its colors are blue and silver.  And House Eldin is associated with Power; its colors are red and black.

\subsubsection*{The Battle of Katmeers:} The climactic final battle against Thevardra’s Endless was fought in the Great Hall of Katmeers itself.  Almost all of you fought in the battle, holding back the Endless while \cHarry{} dueled Thevardra in the middle of the room.  The two of them pulled titanic amounts of magic into themselves as they fought; at the moment they died, all of the energy was unleashed in a cataclysmic arcane backlash that swept over the battlefield.  Many of your classmates were slain by the unleashed energy; many more went insane.

\subsubsection*{Muggles:} People who have no ability to cast magic and are thus not part of the wizarding world.  They are generally oblivious to the existence of magic, a fact which is reinforced by the Veil.

\subsubsection*{The Veil:} A complex arrangement of powerful spells that shield the world of magic from the world of the Muggles, mostly by means of illusions and invisible physical barriers, as well as a few charms of forgetting for insurance.  A very few rare Muggles are able to ignore the Veil, due to close association with a wizard, e.g. the unmagical parents of a wizard child, the unmagical child of wizard parents, or most rare of all, a wizard's Muggle spouse.  The Veil exists due to the general Muggle fear and distrust of the supernatural; before its institution many centuries ago, there were many unpleasant incidents involving pitchfork waving mobs and bonfires, which no one wants to see repeated.

\subsubsection*{The Ministry of Magic:} The governing body of the wizarding world, charged with regulating magic and protecting the citizenry from Dark Wizards and other arcane horrors.  The guardianship of the Veil is also their sacred charge.  The Ministry is presided over by the Minister of Magic, who is elected every ten years by a council of sages; the Minister's powers are roughly on par with that of the Mayor of San Francisco.  The current Minister is your classmate, \cRon{}.

\subsubsection*{The Aurors:} Something of a police force for the wizarding world, the Aurors are tasked with hunting down and stopping Dark Wizards (warlocks, necromancers, specialists in poisons or mind control - you get the idea) wherever they lurk.


\end{document}
