\documentclass[white]{NeptuneBall}
\begin{document}
\name{\wInheritance{}}

\emph{This is a copy of the official ``Line of Succession'' document, available in \sMuseum{}. (This is an in game, transferable item)}

It may come to pass that the currently confirmed or acting ruler of \pAtlantis{} dies or is otherwise found unfit to rule. This can come about in a number of ways. They could be found mentally unstable, demonstrated to have usurped power from the rightful heir, be an illicit form of magical creature (such as a shapeshifter), or be proven to have committed treason. The supreme justice, judge of the highest court of the land may be summoned (find a GM or NPC) to verify any claim that the ruler is unfit. If any of these conditions can be proven to have come to pass, the monarch is then immediately removed. 

To determine who is next in line of succession, follow the list below until you find the first eligible candidate. Assume all classifications that could have multiple members (more than one male child for example) process in order of age. Women who marry into another line of succession forfeit their position in line for the throne of their old kingdom. Bastards of proven lineage are eligible. For example, a bastard cousin is considered in the line of succession as appropriate.

From the last \emph{confirmed} (not acting) ruler of \pAtlantis{} power passes to:

\begin{enumerate}
\item Male children
\item Female children
\item Husband or Wife
\item Brothers 
\item Sisters
\item Brothers-in-law
\item Sisters-in-law
\item The Father
\item The Mother
\item Uncles on the {\bf Father’s} side
\item Uncles on the {\bf Mother’s} side
\item Aunts on the {\bf Father’s} side
\item Aunts on the {\bf Mother’s} side
\item Male cousins on the {\bf Father’s} side
\item Male cousins on the {\bf Mother’s} side
\item Female cousins on the {\bf Father’s} side
\item Female cousins on the {\bf Mother’s} side
\end{enumerate}

If for some reason, no eligible candidate can be  found, the Council of Advisors will elect a new monarch in a closed meeting as soon as possible. (out of the scope of the game)

If power passes to a new person, the acting monarch is considered only a steward until confirmed. If the discredited person manages to reestablish their eligibility before the acting monarch is confirmed they can re-assume power immediately. The process of actually confirming the monarch takes about a week and is the duty of the Council of Advisors.

In order to pass power to the acting monarch:
\begin{enumerate}
\item The supreme justice must preside over the ceremony
\item The eligibility of the candidate must be verified by at least 2 \pAtlantis{}ns (using the chart above).
\item They need to take an oath to protect \pAtlantis{} in front of 3 witnesses (at least 1 must be \pAtlantis{}n).
\end{enumerate}

Following the completion of the ceremony, NPC pages will inform everyone in game of the change.

\iTrident{} rightfully belongs to the acting ruler of \pAtlantis{}. The acting monarch should not hesitate to use his or her extensive authority to acquire  \iTrident{} if anyone is foolish enough to withhold it.

\end{document}
