%%%%%
%%
%% Research Notebooks live in this directory.  This file doubles as a
%% latex'able example notebook.
%%
%% Notebook macros (in ../Lists/notebook-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \startnotebook{...}
%% probably should be the macro for the given whitesheet.  However,
%% you can also just use \name{Some Text} if you want.
%%
%% Note that every \startnotebook command needs a matching
%% \endnotebook command.  Also note that no ownership information
%% appears on the notebook.
%%
%%%%%

\documentclass[greennotebook]{NeptuneBall}
\begin{document}

%\item 
%\item 

\startnotebook{\nGazaStrip{}}

\begin{page}{first}

Your family has recently discovered a great wealth of pearl bearing clams in the \pGazaStrip{}. It is unfortunate that the land is under dispute in the treaty discussions tonight. It is part of why you agreed to attend the \cExExKing{} Ball. You intend to secure this land for \pAtlantis{}. Your family will have no trouble monopolizing the land once it is secure. 

To accomplish this, you will have to figure out why the \pPacifica{}n's care so damn much about the land -- surely they don't know about the pearls? Go and make at least 2 \pPacifica{}ns tell you why the \pGazaStrip{} is so important to them. Once you do so, turn to page \nbref{second}.

\end{page}

\begin{page}{second}

The only thing worse than fighting someone who is in it for the money, is fighting someone who is in it for moral reasons. They never know when to quit. Unfortunately, it looks like the \pPacifica{}ns are after the \pGazaStrip{} for moral reasons. Their precious Kraken was supposedly sighted there, not so long ago.

You will need to contact your family and make sure that they are up for this fight. You may have to burn a lot of political capital and take some major risks to pull this off. Write a note to your family (clearly mark the note as an ``in game'' item) and deliver it to envelope 1 of the ``\sFamily{}'' sign in the entry way. This represents sending the note off with a messenger. You may return 20 minutes later and take the item from envelope 2. Once you have \iCipherLetter{}, turn to page \nbref{third}.

\end{page}

\begin{page}{third}

Your family has of course written to you in code, just in case the letter was intercepted. The letter indicates that the land is of great importance to your family, and they are more than willing to take the risks involved with securing the land. 

Well, if they are determined, then you'd better set things in motion. First thing's first, talk to \cPlant{} and convince \cPlant{\them}, head of the Explorer's Guild, to make a formal (written) declaration that the Explorer's Guild will veto any treaty that does not secure the \pGazaStrip{} for \pAtlantis{}. If \cPlant{\they} is currently indisposed, or refuses to cooperate, you may forge such a document yourself using your ``\aForge{}'' ability. Be careful though, if you are caught forging \cPlant{}'s signature, the dungeons will be the least of your worries.  Once you have the real or forged document in hand, turn to page \nbref{fourth}.

\end{page}

\begin{page}{fourth}

Now to convince the \cKing{\King}. Present the document to \cKing{\King} \cKing{}. Make it very clear to \cKing{\them} that the Explorer's Guild is a crucial part of these negotiations and that \cKing{\they} cannot afford to ignore your demands. Use this fact throughout the evening to delay the treaty if you haven't completed your research and the treaty doesn't give you what you want. Once you have presented the document to \cKing{}, turn to page \nbref{fifth}.

\end{page}

\begin{page}{fifth}

Now for the real digging. Go through the papers in ``\sPrince{}'', and find out more specifics about this giant squid sighting. You will need to take the ``\iReference{}'' item from the room. Once you have find a date for the sighting, and the person who sighted it, turn to page \nbref{sixth}.

\end{page}

\begin{page}{sixth}

Okay, you have a date (\cKraken{\MYname}). Now to prove that the Kraken was elsewhere. Legend has it that the Kraken causes shipwrecks on a regular basis. Well, if anyone would know, it would be the Explorer's Guild. Go and check their files and journals. (You may take ``\iNorthSeasJournal{}'' from ``\sJournals{}'' in the Explorer's Guild.)  turn to page \nbref{seventh}.

\end{page}

\begin{page}{seventh}

Good progress. Now the nail in the coffin. Find out who \cLiar{\MYname} is. Hopefully he's got some petty criminal record that you can trump up. Spend 1 minute searching each bookshelf in ``\sMuseum{}''. Once you have searched all 3 bookshelves, you may take ``\iRapSheet{}'' from the bookshelf that your $\gamma$ stat allows you to access, then turn to page \nbref{eighth}.

\end{page}

\begin{page}{eighth}


Gold. \cLiar{\MYname} has a rap-sheet as long as your uncle's (who is serving life after getting careless during a heist). \cLiar{} is a con artist, and has been for decades. Use ``\iNorthSeasJournal{}'', ``\iRapSheet{}'', and the ``\iReference{}'' from \cPrince{}'s own papers to convince the \pPacifica{}ns that they have been lied to. Hopefully this will be enough to loosen their demands on the land.

\end{page}


\endnotebook

\end{document}
