%%%%%
%%
%% Research Notebooks live in this directory.  This file doubles as a
%% latex'able example notebook.
%%
%% Notebook macros (in ../Lists/notebook-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \startnotebook{...}
%% probably should be the macro for the given whitesheet.  However,
%% you can also just use \name{Some Text} if you want.
%%
%% Note that every \startnotebook command needs a matching
%% \endnotebook command.  Also note that no ownership information
%% appears on the notebook.
%%
%%%%%

\documentclass[greennotebook]{NeptuneBall}
\begin{document}

%\item 
%\item 

\startnotebook{\nIllicitWeapons{}}

\begin{page}{first}

You need to contact the \pAtlantis{}n mole. Find a way to talk to \cGeneral{} alone and convince \cGeneral{\them} to let you examine the weapon.

Once you have examined the \iPrototype{} for at least 2 minutes, turn to page \nbref{second}.

\end{page}

\begin{page}{second}

These are definitely the weapons you need to turn the tide of the war. Seal the deal with \cGeneral{}, hand over the \iBattlePlan{}, and get the \iPrototype{}. You'll need to confer with \cGeneral{\them} later to coordinate a plan of attack after \cGeneral{\they}'s had a chance to look over the document.  

Once at least 20 minutes have passed, turn to page \nbref{third}.

\end{page}

\begin{page}{third}

Something's bugging you. You might've been a little hasty in declaring this weapon viable. Maybe you'd better test this prototype. Go to \sGardens{} and spend 2 minutes shooting the prototype weapon. Role play accordingly.

Once you have finished testing the weapon, turn to page \nbref{fourth}.

\end{page}

\begin{page}{fourth}

Something doesn't feel quite right, and something is nagging at your mind about the way it fires. Go talk to a weapons expert like \cPrince{}, a mature human, or a powerful magician about the weapon. You will have to show them the \iPrototype{}. 

Once you have had this discussion, turn to page \nbref{fifth}.

\end{page}

\begin{page}{fifth}

From their reaction, it's clear - something isn't quite right. But what? Go and do some research in the library and see if you can find any blueprints to compare these to. Spend 1 minute searching each bookshelf in the library. Once you have searched all 3 bookshelves, turn to page \nbref{sixth}

\end{page}

\begin{page}{sixth}

Now that \emph{is} devious. Only someone as clever as you could have spotted this before half of the \pPacifica{}n army was armed with these time bombs! That \cGeneral{} lied to you, and \cGeneral{\they}'s been lying to your superiors too - \cGeneral{\they}'s no traitor to \pAtlantis{}! And now, \cGeneral{\they} has the \iBattlePlan{\MYname}! Retrieve the \iBattlePlan{} from \cGeneral{\them} - and find some way to end \cGeneral{\their} threat to \pPacifica{} - permanently.

\end{page}

\endnotebook

\end{document}
