%%%%%
%%
%% Research Notebooks live in this directory.  This file doubles as a
%% latex'able example notebook.
%%
%% Notebook macros (in ../Lists/notebook-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \startnotebook{...}
%% probably should be the macro for the given whitesheet.  However,
%% you can also just use \name{Some Text} if you want.
%%
%% Note that every \startnotebook command needs a matching
%% \endnotebook command.  Also note that no ownership information
%% appears on the notebook.
%%
%%%%%

\documentclass[greennotebook]{NeptuneBall}
\begin{document}

%\item 
%\item 

\startnotebook{\nIndianAggression{}}

\begin{page}{first}

You have been talking to \cPrince{} for months about \pIndia{}, but \cPrince{\they} doesn't believe you. You'd better test the waters in \pAtlantis{} and figure out if the monarchy here is any more receptive. Talk to \cKing{}, or whoever is the current ruler of \pAtlantis{}, for 3 minutes about \pIndia{}n aggression. Once you've learned what \pAtlantis{} thinks about \pIndia{}, turn to page \nbref{second}.

\end{page}

\begin{page}{second}

Opposition at every turn. \pAtlantis{} is just as oblivious as \pPacifica{}. You must find proof to show \cPrince{} and \cKing{} to prove the impending danger to them. If only you could scry on \pIndia{}! But those spells take weeks to prepare. You have mere hours. Maybe \pAtlantis{} has a magical item that could help you? Go do some research in the library. Spend 1 minute searching each bookshelf in the library. Once you have searched all 3 bookshelves, turn to page \nbref{third}.

\end{page}

\begin{page}{third}

You found tell of a scrying mirror, \iScryingMirror{}. This mirror is here in the archives and should allow you to scry, as long as you know the location you want to scry on. You will have to gather more information. Try talking to \cGeneral{} since \cGeneral{\they} is part of the Guardian's guild. (If \cGeneral{} is unavailable, you may go through \cGeneral{\their} papers instead). Find out what information \cGeneral{} has on where an army might mass troops for war. Spend 2 minutes trying to gather this intelligence. Once you have done so, turn to page \nbref{fourth}.

\end{page}

\begin{page}{fourth} %%% MAKE HER DOCUMENTS!

\cGeneral{} said something that reminds you of some of your own research. Return to your quarters and look through your documents until you find the name of the plateau south east of the Tasmanian Sea. Once you know it's name, turn to page \nbref{fifth}.

\end{page}

\begin{page}{fifth}

Well, you have a name now. All you need are coordinates. Where could you find a map? \pPacifica{} has never been on good terms with \pIndia{} and so has very few maps. The Explorer's Guild of \pAtlantis{} might have better maps. Get into the Explorer's Guild and take a \iMapOfIndia{}. (You may take a map of your choice from the ``\sPileOfMaps{}'' sign) Then, turn to page \nbref{sixth}.

\end{page}

\begin{page}{sixth}

Things are falling into place. Next you will need something to power the mirror with, aside from your own magic. Acquire an \iElectricEel{}. Once you have it, turn to page \nbref{seventh}.

\end{page}

\begin{page}{seventh}

Now that you know where to scry, and how you will power the mirror, you just need access to \iScryingMirror{}. Either persuade \cKing{\King} \cKing{}, or whoever else is ruling \pAtlantis{} at the moment, to let you borrow it, or follow the directions on ``\sArtifactThree{}'' to break in and take the mirror. Once you are in possession of \iScryingMirror{} turn to page \nbref{eighth}.

\end{page}

\begin{page}{eighth}

Acquire some \iChalk{} and trace the ``\sRunicCircle{}''. This action activates the circle and prepares it to support a magician through a difficult spell. If the circle is already chalked, you must first remove the old chalk.

Once you have prepared the circle, spend 2 minutes meditating undisturbed (this action is interruptible) in the middle of the circle to scry in the mirror. Once you have finished meditating, {\bf open \iScryingMirror{}} and turn to page \nbref{ninth}

\end{page}

\begin{page}{ninth}

This is finally what you need to convince \cKing{} and \cPrince{}! Hurry and do so before it is too late. You must persuade them to include a military alliance in the treaty!

\end{page}


\endnotebook

\end{document}
