%%%%%
%%
%% Research Notebooks live in this directory.  This file doubles as a
%% latex'able example notebook.
%%
%% Notebook macros (in ../Lists/notebook-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \startnotebook{...}
%% probably should be the macro for the given whitesheet.  However,
%% you can also just use \name{Some Text} if you want.
%%
%% Note that every \startnotebook command needs a matching
%% \endnotebook command.  Also note that no ownership information
%% appears on the notebook.
%%
%%%%%

\documentclass[greennotebook]{NeptuneBall}
\begin{document}

%\item 
%\item 

\updatemacro{\cWitch}{
  \nickname{Ursula}
  \mapnickinformal
}

\startnotebook{\nSpellBreakNotebook{}}

\begin{page}{first}

Do not open this notebook to page 2 until instructed to do so.

%3 people to perform a pactbreaker ritual (requires being knocked out)

\end{page}

\begin{page}{second}

You've kicked the first layer of the spell, but the second layer is still in place. If you want to get your revenge, you'll need to break it. All those years ago, \cWitch{} forced you into a magical contract against your will - but unfortunately, that doesn't make it any less binding.

You know that there are some characters around here that are less than scrupulous. Maybe they know how to get out of a magical contract? Talk to a current or former member of the Assassin's Guild for one minute. They can help you. Once you have done so, open the next page.

\end{page}

\begin{page}{third}

That was quite informative. Apparently the bonds of magical contracts aren't nearly as strong when performed by an unwilling participant. You need to perform something known as a Pactbreaker Ritual in order to escape it. You've heard of this ritual - though you never thought it would apply to your situation so easily! The ritual is fairly simple, and can be done without any magical skill, but requires several items, and the assistance of 3 people you trust.

To begin with, find a \iClam{} (open or closed doesn't matter) and a \iSeaFan{}. You're pretty sure that you're only going to find those in natural places. Once both are in hand, open the next page.

\end{page}

\begin{page}{fourth}

Securing a blessing before the ritual is supposed to make it a lot safer. Seek a blessing from a priest. If none are available, a blessing from the current ruler of \pAtlantis{} will do, but this might make the ritual more dangerous. (If they don't know how to perform a blessing, tell them out of character that they can make one up). Once you have received some kind of blessing, turn to the next page.

\end{page}

\begin{page}{fifth}

You're finally ready to begin the ritual! Gather 3 people to help you, and find a secluded place. Meditate on your contract for 1 minute while the others chant ominously around you. At the end of that minute, have two of them assist the third in a knockout attack on you.

Once you wake up from being knocked out, turn to the next page.

\end{page}

\begin{page}{sixth}

That's it! You've done it! You can feel the curse lifting, and your actions becoming your own once again! Remove your \iIdentityProtectionSpell{} magical effect, and take your revenge!

\end{page}

\endnotebook

\end{document}
